Mutual Information Plots

### 2025-12-12 mutual_information_curves.qmd

weighted_kendall(c(1,1,1,1,5,6), k = 3, r = c(1,1,1,1,5,6))
# Only works for k = # of top teams tied

@@

# Combine across all k
rhat_df <- bind_rows(all_results)
```

@@

    }
  #}
  #w <- 1 / (w+1)  # Inverse of squared differences and manually change 0 probabilities to 1 on the inverse
  #w <- w/sum(w)
  # Compute weights dynamically for each row
  weighted_df <- prob_df %>%
    mutate(w = w)

>>>>

@@

# Combine across all k
rhat_df <- bind_rows(all_results)
rhat_df %>% filter(k==1)
```

@@

    }
  #}
  #w <- 1 / (w+1)  # Inverse of squared differences and manually change 0 probabilities to 1 on the inverse
  #w <- w/sum(w)
  # Compute weights dynamically for each row
  weighted_df <- prob_df %>%
    mutate(w = w)
  print(weighted_df)
